\LARGE \bf \pyRobots, a toolkit for robot executive control

### 2014-09-04 paper.tex
Added a screenshot of Anahita's log analyser
Commented out the full example. Not very useful in such a paper

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Detailed Example}

\begin{pythoncode}
    import time
    from robots import GenericRobot
    from robots.decorators import action, lock
    from robots.resources import Resource
    from robots.signals import ActionCancelled

    # create a 'lockable' resource for our robot
    WHEELS = Resource("wheels")

    class MyRobot(GenericRobot):

      def __init__(self):
        super(MyRobot, self).__init__()

        # create (and set) one element in the robot's state.
        # Here a sonar.
        self.state["sonar"] = 10.

        # do whatever other initialization you need :-)

      def send_goal(self, pose):
        # move your robot using your favorite middleware
        print("Starting to move towards %s" % pose)

      def stop(self):
        # stop your robot using your favorite middleware
        print("Motion stopped")

      def whatever_lowlevel_method_you_need(self):
        pass

    @lock(WHEELS)
    @action
    def move_forward(robot):
      """ Actions are written in a simple imperative, 
          blocking style.
      """

      # the target pose: simply x += 1.0m in the robot's 
      # frame. pyRobots will handle the frames 
      # transformations as needed.
      target = [1.0, 0., 0., "base_link"]

      try:
        robot.send_goal(target)

        while(robot.pose.distance(robot.pose.myself(), 
                                  target) > 0.1):
            # robot.sleep is exactly like time.sleep, 
            # except it lets the pyrobots signals pass 
            # through.
            robot.sleep(0.5)

        print("Motion succeeded")

      except ActionCancelled:
        # if the action is cancelled, clean up your state
        robot.stop()

    with MyRobot() as robot:

      # Turn on DEBUG logging.
      # Shortcut to configure the std Python logging system
      robot.debug()

      robot.whenever("sonar", below = 0.3).do(move_forward)

      try:
        while True:
          time.sleep(0.5)
      except KeyboardInterrupt:
        pass
\end{pythoncode}
\caption{Full example of a \pyRobots application.}
\label{mwe}
\end{listing}

@@

\paragraph{Stress-test in a nursery}

@@

\begin{itemize}
    \item control mixing policies?
    \item control over action priorities
    \item path to more complex control tool (T-REX, etc)
\end{itemize}

>>>>

\begin{figure}
        \centering
        \includegraphics[width=0.9\columnwidth]{log}
        \caption{Screenshot of \pyRobots log analyser, processing the log of the
        experiment presented at section~\ref{croq}}
        \label{log_view}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \section{Detailed Example}
% 
% \begin{listing}[h!]
% 
% \begin{pythoncode}
%     import time
%     from robots import GenericRobot
%     from robots.decorators import action, lock
%     from robots.resources import Resource
%     from robots.signals import ActionCancelled
% 
%     # create a 'lockable' resource for our robot
%     WHEELS = Resource("wheels")
% 
%     class MyRobot(GenericRobot):
% 
%       def __init__(self):
%         super(MyRobot, self).__init__()
% 
%         # create (and set) one element in the robot's state.
%         # Here a sonar.
%         self.state["sonar"] = 10.
% 
%         # do whatever other initialization you need :-)
% 
%       def send_goal(self, pose):
%         # move your robot using your favorite middleware
%         print("Starting to move towards %s" % pose)
% 
%       def stop(self):
%         # stop your robot using your favorite middleware
%         print("Motion stopped")
% 
%       def whatever_lowlevel_method_you_need(self):
%         pass
% 
%     @lock(WHEELS)
%     @action
%     def move_forward(robot):
%       """ Actions are written in a simple imperative, 
%           blocking style.
%       """
% 
%       # the target pose: simply x += 1.0m in the robot's 
%       # frame. pyRobots will handle the frames 
%       # transformations as needed.
%       target = [1.0, 0., 0., "base_link"]
% 
%       try:
%         robot.send_goal(target)
% 
%         while(robot.pose.distance(robot.pose.myself(), 
%                                   target) > 0.1):
%             # robot.sleep is exactly like time.sleep, 
%             # except it lets the pyrobots signals pass 
%             # through.
%             robot.sleep(0.5)
% 
%         print("Motion succeeded")
% 
%       except ActionCancelled:
%         # if the action is cancelled, clean up your state
%         robot.stop()
% 
% 
%     with MyRobot() as robot:
% 
%       # Turn on DEBUG logging.
%       # Shortcut to configure the std Python logging system
%       robot.debug()
% 
%       robot.whenever("sonar", below = 0.3).do(move_forward)
% 
%       try:
%         while True:
%           time.sleep(0.5)
%       except KeyboardInterrupt:
%         pass
% \end{pythoncode}
% \caption{Full example of a \pyRobots application.}
% \label{mwe}
% \end{listing}
%

@@

\paragraph{Stress-test in a nursery}
\label{croq}

@@

\begin{itemize}
    \item control mixing policies?
    \item control over action priorities
    \item path to more complex control tool (T-REX, etc)
    \item investigate techniques in Python's {\sc asyncio} module
\end{itemize}
